Sexual selection improves population fitness: a meta-analysis

### 2018-12-19 Response_to_Nature_Comms.Rmd

load(".RData")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Dear Dr. Jones and colleagues,

Many thanks for your time, and for the very helpful comments on our manuscript. We have considerably reworked the manuscript in light of the many insightful comments and suggestions provided by the reviewers. Please see below for a detailed list of responses to each of the reviewers' points.

We also attach a revised manuscript and a revised copy of the supplementary material, as well as a copy of the revised manuscript in which the significant changes and additions have been highlighted. Please let us know if we can do anything further to assist you.

Finally, in addition to the changes suggested by reviewers, we discovered a small number of errors in our original analysis, related to how effect sizes were calculated from certain primary studies in our meta-analysis. As such, we have thoroughly rechecked our dataset and re-ran the analyses with all errors corrected. **XXXXXXXXX**

@@

Answer

**Other comments:**

>*l. 30 – reviews on sexual conflict are OK to cite here, but there are empirical papers actually demonstrating correlation between male sexual selected traits (Harano et al. 2011; Plesnar et al. 2014) which should also be cited.*

Thank you, we have added citations of those papers as suggested.

@@

>*l. 151 – the authors discuss beneficial effects of sexual selection on direct fitness measures such as reproductive success or offspring viability, but estimates for both of these measures actually overlapped zero! Perhaps joint analysis of direct fitness measures, as I suggested above, could support this conclusion, but currently this is an overstatement.*

Thank you for catching this -- we have tempered our conclusions in the relevant section of the Discussion, since the results provide only moderate evidence for a positive effect of sexual selection on these traits.

@@

>*In the discussion the authors say they included the number of experimental evolution generations, but I could not find this information in methods.*

This information could be found in the supplementary material in the section *Meta-analyses including many moderator variables* as well as in Figure S12 and S13. Generations (specifically, log-Generations) had minimal effect on the effect sizes and so was removed for the "minimum adequate models" that we presented in the main text. **We now clarify this in the main text JUSTIN, MAYBE REFERENCE THOSE FIGURES WHEN SAYING IT'S NON-SIG OR SOMETHING LIKE THAT**.

@@

>*Fig. S1 is not referred to in the main texts, is it different from Fig. 2, except that the latter contains predicted average values for fitness components?*

Our supplementary material does indeed contain all of our main figures, in order to show the data and code used to generate them. We have now made sure that e.g. Figure 2 in the HTML supplement is correctly labelled as Figure 2, to make it clear that it is not a different figure. **A JOB FOR JUSTIN HERE**

@@

>*As a response, they come up with log response ratio (lnRR) - see*

>Hedges, L. V., J. Gurevitch, and P. S. Curtis. 1999. The meta-analysis of response ratios in experimental ecology. \textit{Ecology} 80:1150-1156.

>*I recommend that the authors use lnRR for their effect size for mean comparison as well as Hedge's $g$ to see the robustness of their conclusions for the mean.*

Reviewer 2 is correct that Hedges' *g* is imperfect, and so we extended our meta-analysis to include two alternative measures of effect size. Firstly, we present the log response ratio (*lnRR*) as suggested by this reviewer. Secondly, we present a modified version of Hedges' *g* that attempts to account for this heterogeneity issue [@bonett2009meta], named SMDH (standardized mean difference with heteroscedastic population variances in the two groups). There are several key findings from our new analyses using lnRR and SMDH:

*Firstly*, Hedges' *g* and SMDH are highly correlated (in means and variance). This suggests that unequal variance between the treatment and control groups (heteroscedasticity) in the primary studies we examined is probably too small to greatly influence Hedges' *g*, which is interesting for the interpretation of earlier meta-analyses using Hedges' *g*.

@@

```{r, warning=FALSE, message = FALSE, error=FALSE}
#This function writes in the correlation value
panel.cor <- function(x, y, digits=2, prefix="", cex.cor, ...)
{
  usr <- par("usr"); on.exit(par(usr))
  par(usr = c(-2.5, 2.5, -2.5, 2.5))
  r <- cor(x, y, use="pairwise.complete.obs")
  txt <- format(c(r, 0.123456789), digits=digits)[1]
  txt <- paste0(prefix, txt)
  if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
  text(0, 0, txt, cex = cex.cor * 2*r)
}

es.correlation.df <- lnRR.data %>% left_join(SMD.data %>% rename(`Hedge's g` = SMD)) %>% left_join(SMDH.data)

pairs(es.correlation.df %>% select(`Hedge's g`, lnRR, SMDH), lower.panel=panel.smooth, upper.panel=panel.cor)
# pairs(es.correlation.df %>% select(SMD_var, SMDH_var), lower.panel=panel.smooth, upper.panel=panel.cor)
```

*Secondly*, we note that lnRR and SMDH can only be calculated in cases where the primary study reported means, standard deviations and sample sizes (352 out of 459). This is a limitation, as we must discard roughly 25% of the data in order to use lnRR and SMDH, and so we think it is worthwhile to focus primarily on Hedges' *g* despite its minor limitations in the main manuscript, and use lnRR and SMDH for sensitivity analysis (to verify that the results are qualitatively the same as those produced by Hedges' *g*).

@@

```{r, warning=FALSE, message = FALSE, error=FALSE}
predictions.complete2 %>% select(Sex, Environment, `Hedge's g sample size` = n) %>% 
  left_join(predictions.lnRR %>% select(Sex, Environment, `lnRR sample size` = n), by = c("Sex", "Environment")) %>%
  adorn_totals("row") %>% pander()
```

*Thirdly*, if we conduct a meta-analysis using lnRR as the effect size we obtain very similar results with all our main conclusions unchanged, keeping in mind that lnRR and Hedge's are on different scales (see the revised Supplementary Material). Specifically,
+ The effect of sexual selection on population fitness is generally positive.
+ This effect is magnified for females in stressful environments with a significantly positive interaction term (stress*females).

@@

```{r, warning=FALSE, message=FALSE, error = FALSE, fig.align='center', fig.width = 10, fig.height=6}
grid.arrange(both.plots + 
               guides(fill = FALSE) + 
               ggtitle("Comparison between Hedge's g \nand lnRR effect sizes \n"), 
             lnRR.plots + ggtitle("\n\n") + xlim(-0.5,0.75), nrow = 1, widths = c(3,4))
```

*Fourthly*, the distribution of the lnRR effect sizes is non-normal (notably moreso than the distribution of Hedges' *g*), perhaps because one can get extreme values when taking a ratio (e.g. when the denominator is close to zero). Accordingly, @Lajeunesse_2015 showed that *lnRR* is problematic when quantifying the outcome of primary studies with small sample sizes, and can yield unsuitable variance estimates when the parameter scale of the study are close to zero. So, Hedges' *g* has the possible practical advantage of increasing model fit in our meta-analysis.

@@

>*2 --- The authors may consider also doing another set of meta-analyses using lnVR (log variability ratio - proposed in Nakagawa et al. 2015).*

>Nakagawa, S., R. Poulin, K. Mengersen, K. Reinhold, L. Engqvist, M. Lagisz, and A. M. Senior. 2015. Meta-analysis of variation: ecological and evolutionary applications and beyond. \textit{Methods in Ecology and Evolution} 6:143-152.

>*As one can see in Figure 2, the mean results (Hedges' $g$) are a mirror image of the variance results (this makes sense CV controls for means). I would like to see what the absolute change in variances. Probably the authors can put the analysis using lnVR in the supplement. The results of this analysis can be discussed. Also, the mean-variance relationship between mean and variance (sd) should be verified (e.g. plot log mean and log sd or log variance).*

Many thanks -- we have now also present a meta-analysis of variation using lnVR in addition to one using lnCVR. We have the following comments on this new analysis:

*Firstly*, as the reviewer suggested, we now justify our use of lnCVR as opposed to lnVR, by assessing the mean-variance relationship in our data. The major limitation of lnVR is that it does not account for the mean-variance relationship; indeed this is why lnCVR was suggested as the favourable correction [@RN177]. We indeed found a strong positive correlation between mean and variance, suggesting our original use of lnCVR was justified.

@@

```{r, warning=FALSE, message=FALSE, error = FALSE, fig.align='center', fig.width = 8, fig.height=3.75}
grid.arrange(full_dataset %>% ggplot(aes(x = mean.low, y = sd.low))+
  geom_point()+
  scale_x_log10()+
  scale_y_log10()+
  xlab("Mean of Control Group")+
  ylab("Standard Deviation of Control Group") +
  geom_smooth(method = "lm", colour = "red"),

  full_dataset %>% ggplot(aes(x = mean.high, y = sd.high))+
  geom_point()+
  scale_x_log10()+
  scale_y_log10()+
  xlab("Mean of Treatment Group")+
  ylab("Standard Deviation of Treatment Group") +
  geom_smooth(method = "lm", colour = "red"), nrow = 1)
```

*Secondly*, We conducted new Bayesian and REML meta-analyses for *lnVR*, which we present in the supplementary material and briefly discuss in the manuscript. We found a similar trend for the meta-analysis of variance using *lnCVR* and the meta-analysis of variance using *lnVR*, These are:

@@

>Nakagawa, S., and E. S. A. Santos. 2012. Methodological issues and advances in biological meta-analysis. \textit{Evolutionary Ecology} 26:1253-1274.

>*This is what the authors use. Also, it will be good to put the degree in I^2 in the context. To do this see this paper:*

>Senior, A. M., C. E. Grueber, T. Kamiya, M. Lagisz, K. O'Dwyer, E. S. A. Santos, and S. Nakagawa. 2016. Heterogeneity in ecological and evolutionary meta-analyses: its magnitude and implications. \textit{Ecology} 97:3293-3299.

Many thanks for this feedback -- we have incorporated all the suggestions within a paragraph in the Methods section.

@@

>*4 --- Publication tests have been conducted on, I think, "meta-analytic" residuals results as suggested in Nakagawa and Santos 2012. One could use such residuals to conduct the trim and fill method and see how much the mean could move (see Nakagawa and Santos 2012). One should remember the funnel asymmetry could be caused by the presece of heterogeniety. See:*

>Egger, M., G. Smith, M. Schneider, and C. Minder. 1997. Bias in metaanalysis detected by a simple, graphical test. \textit{Br Med J} 315:629 - 634.

Thanks -- we now remind the reader that funnel plot asymmetry is not decisive evidence for publicaiton bias, because it can also result from unexplained heterogeneity in the original effect sizes. We have elected not to implement trim-and-fill since the method seems to have fallen into disfavour among many readers, and because we are unsure how to correctly implement it using the REML- and Bayesian methods we used. NB that there is no method for trim-and-fill in mixed meta-analysis in the popular R package `metafor` (which we used), suggesting the method is not simple to implement.

@@

>*5 --- Figure 3 - are these grey envelopes 95% CI?*

Yes, and we have now included this information in the figure caption. Thank you for highlighting this.

@@

>*6 --- the title - do the authors include "a systematic review" - so "a systematic reveiw and meta-analysis" - these two things are diferent - see:*

>Nakagawa, S., and R. Poulin. 2012. Meta-analytic insights into evolutionary ecology: an introduction and synthesis. \textit{Evolutionary Ecology} 26:1085-1099.

We think that the scope of a true systematic review (in the sense used by e.g. Cochrane reviews) is larger than our study entails. However, we did use a systematic literature search strategy and PRISMA framework of inclusion/exclusion. With this in mind, we have left our paper's title as "meta-analysis" rather than calling it a systematic review.

### 2018-12-28 Response_to_Nature_Comms.Rmd

load(".RData")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Dear Dr. Jones and colleagues,

Many thanks for your time, and for the very helpful comments on our manuscript. We have made many changes in light of the three reviewers' detailed feedback, and we feel that the manuscript has been greatly improved. Please see the letter below for our detailed responses to each of the reviewers' points. In addition to the revised manuscript and revised supplementary material, we attach a copy of the revised manuscript in which the significant changes and additions have been highlighted.

Finally, while working on the revisions we discovered a small number of errors, namely that we had miscalculated effect size from certain types of primary data. As such, we have thoroughly rechecked our dataset and re-ran all analyses with the errors corrected. **XXXXXXXXX**

@@

________________________________________________________

## Comments from Reviewer 1 (Prof. Jacek Radwan)

>*The manuscript presents results of a meta-analysis assessing the effect of sexual selection on population fitness. This topic has been increasingly studied over the past decade or so, and the time seems ripe for a synthesis. The authors have done good job searching the literature – it includes all relevant papers I could remember, and the results should be of interest to a broad range of evolutionary biologists. I cannot expertly judge on state-of-the-art methodology, but I do have several general concerns about how the analyses were performed.*

Many thanks for your time and for you very helpful feedback.

@@

>*Firstly, it seems that several male traits like to be under sexual selection, but not related to population fitness were included. I don’t think this is correct given the question being asked (i.e. whether sexual selection increases population fitness). I think traits which are directly under sexual selection (eg. attractiveness, reproductive success) should not be pooled with traits which may respond to manipulation of sexual selection indirectly (eg. male development time, survival) and can affect population fitness. Distinguishing between both types of trait could actually be revealing – e.g. could expose trade-offs between sexually selected traits and fitness components unrelated to reproductive competition (see eg. Radwan et al. 2015 Evol Biol), a thus potentially explain lower effect of sexual selection on (pooled) male traits than on female traits.*

We completely agree that male attractiveness does not affect population fitness directly, and it is important that this is reflected in the meta-analysis. In the study, we took this belief into account.  Specifically, we recorded effect size estimates relating to attractiveness (for completeness, and because it is possible that attractiveness is genetically correlated with traits that *do* affect population fitness). However, we classified male attractiveness as having an "indirect" relationship with population fitness (we did the same for other traits too, such as body condition and life span; see Table S1 for a full breakdown). However on reflection, we think that attractiveness is even more tenuously linked to population fitness, and so we have re-classified it as "ambiguous", along with traits like "Immunity" and "Development rate". Our main analysis excludes all of the ambiguous traits, and so our main results are now not derived from any effect sizes relating to male attractiveness. The exclusion of the n = 6 attractiveness effect sizes did not qualitatively change the results.

@@

>*Secondly, looking at Figure 1, one notices apparent anomalies, for example significantly positive slope for male attractiveness, based on studies with average effect size close to zero. I think this (and few others) surprising estimates may result from fitting random terms across all trait types (fitted as a fixed factor, second model); I guess fitting interaction (random slopes) would not be feasible for some categories including few data points, but some of them could easily be pooled in wider categories.*

For reference, we here present the result for male attractiveness that the reviewer mentioned. The table shows the estimate from the meta-analysis, and the figure shows the n = 6 effect sizes that underlie it, with the mean effect size plotted as vertical lines.

@@

  #Add theme specifying text size, margins, lines etc.
  theme_bw()+

  theme(strip.text.y = element_text(angle = 0, size = 12, margin = margin(t=15, r=15, b=15, l=15)), 
        strip.background = element_rect(colour = NULL,
                                        linetype = "blank",
                                        fill = "gray90"),
        text = element_text(size=13),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=12), 
        legend.title=element_text(size=12, 
                                  face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 12))

p.meta.male.attract
```

We agree that alone, these 6 studies do not provide strong evidence the mean is positive, though note that the very precisely measured effect sizes are mostly positive. However the model of the full dataset contains many other effect sizes, with are primarily positive, and so

### 2018-12-29 Response_to_Nature_Comms.Rmd

grid.arrange(both.plots + 
               guides(fill = FALSE)+
               ggtitle("Indirect And Direct\n")+ theme(plot.title = element_text(size = 18, face = "bold", colour = "Red")),
             both.direct.plots + ggtitle("Direct Only\n")+
               theme(axis.title.y = element_blank(), 
                     plot.title = element_text(size = 18, face = "bold", colour = "Red")), 
             nrow = 1, 
             widths = c(3,4))
```

```{r, warning=FALSE}
predictions.direct %>% pander(caption = "Model using only direct measures of fitness")
```

>*Another major problem I have with the manuscript concerns interpretation of the very intriguing finding that the response to manipulation of sexual selection was stronger for female traits compared to male traits. I’m confused by the authors’ explanation: do they assume sexual selection acted directly on females, and not only indirectly, via males? Only then things like mother to daughter heritability, or hard selection on females, should matter.*

We agree that this section could have been much clearer, and have made some changes in light of this comment to clarify what we meant. We believe that experiments that manipuate sexual selection on males will alter female fitness traits, even in species where females experience no sexual selection, because of mechanisms such as intra- and inter-locus sexual conflict. That is, evolution in males will almost always have pleiotropic consequences for females, or change how males males affect females (i.e. sexual selection on males causes of evolution of males' indirect genetic effects on females).

Consider for example the classic Holland and Rice-style experiment, where one removes sexual selection by enforcing random monogamy in a species like _Drosophila_ with 'traditional sex roles'. The males in these experiments are predicted to evolve to be less harmful to females, and they are also predicted to evolve a more female-like overall phenotype, due to the removal of selection on male-specific functions involved in sexual selection. Both of these male adaptations are expected to cause a genetically-based change in female traits: the former as a result of inter-locus coevolution (e.g. female resistance should evolve in response to decreased male harm), and the latter as a result of pleiotropy between the sexes. We thus might predict that females would adapt even more than males if female traits have more genetic variation, or if selection is 'harder' on females than males. These explanations are speculative and _post hoc_, and so in the revision we are careful to identify them as such. This result is arguably opposite to what one would predict, since the removal of sexual selection on males appears to be a more drastic change for males than for females, and we now spell this out as well.

@@

>*l. 30 – reviews on sexual conflict are OK to cite here, but there are empirical papers actually demonstrating correlation between male sexual selected traits (Harano et al. 2011; Plesnar et al. 2014) which should also be cited.*

Thank you, we have added citations of those papers as suggested.

>*l. 151 – the authors discuss beneficial effects of sexual selection on direct fitness measures such as reproductive success or offspring viability, but estimates for both of these measures actually overlapped zero! Perhaps joint analysis of direct fitness measures, as I suggested above, could support this conclusion, but currently this is an overstatement.*

Thank you for catching this -- we have tempered our conclusions in the relevant section of the Discussion, since the results provide only moderate evidence for a positive effect.

@@

>*In the discussion the authors say they included the number of experimental evolution generations, but I could not find this information in methods.*

For relevant results, please see the section of the results that reads "Other moderator variables that we examined had minimal impacts on effect size (Figure S2, Table S10). Specifically, effect size did not depend on whether or not the study was conducted blind (Figure S9), nor on the number of generations for which the experimental evolution study was run (Figure S10, S11)." In the methods, we wrote "Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), blinding of researchers to treatments and number of generations a treatment group underwent experimentally evolution."

@@

>*Fig. S1 is not referred to in the main texts, is it different from Fig. 2, except that the latter contains predicted average values for fitness components?*

Our supplementary material does indeed contain all of our main figures, in order to show the data and code used to generate them. We have changed the numbering of the supplementary figures, so that e.g. Figure 2 in the HTML supplement is correctly labelled as Figure 2 and not as Fig. S1, to make it clear that it is the same figure. **A JOB FOR JUSTIN HERE**

@@

>Nakagawa, S., R. Poulin, K. Mengersen, K. Reinhold, L. Engqvist, M. Lagisz, and A. M. Senior. 2015. Meta-analysis of variation: ecological and evolutionary applications and beyond. \textit{Methods in Ecology and Evolution} 6:143-152.

>*As one can see in Figure 2, the mean results (Hedges' $g$) are a mirror image of the variance results (this makes sense CV controls for means). I would like to see what the absolute change in variances. Probably the authors can put the analysis using lnVR in the supplement. The results of this analysis can be discussed. Also, the mean-variance relationship between mean and variance (sd) should be verified (e.g. plot log mean and log sd or log variance).*

Many thanks -- we have now also present a meta-analysis of variation using lnVR in addition to one using lnCVR. We have the following comments on this new analysis:

*Firstly*, as the reviewer suggested, we now justify our use of lnCVR as opposed to lnVR, by assessing the mean-variance relationship in our data. The major limitation of lnVR is that it does not account for the mean-variance relationship; indeed this is why lnCVR has been recommended over lnVR [@RN177]. We indeed found a strong positive correlation between mean and variance, suggesting our original use of lnCVR was justified.

@@

  full_dataset %>% ggplot(aes(x = mean.high, y = sd.high))+
  geom_point()+
  scale_x_log10()+
  scale_y_log10()+
  xlab("Mean of Treatment Group")+
  ylab("Standard Deviation of Treatment Group") +
  geom_smooth(method = "lm", colour = "red"), nrow = 1)
```

*Secondly*, We conducted new Bayesian and REML meta-analyses for *lnVR*, which we present in the supplementary material and briefly discuss in the manuscript. We found a similar trend for the meta-analysis of variance using *lnCVR* and the meta-analysis of variance using *lnVR*, These are:

+  In stressful environments sexual selection leads to a decrease in the variance for females, relative to benign environments.  
+  Sexual selection reduces variance in females compared to males.

However, when using *lnVR*, the variability of fitness traits for males under sexual selection increased, *lnVR* for females in stressful environments was not statistically different from zero, and sexual selection in benign environments increased phenotypic variance for females. Model results and predictions (from the REML model) can be cound in the Supplementary Material.

@@

Many thanks for this feedback -- we have incorporated all the suggestions within a paragraph in the Methods section.

>*4 --- Publication tests have been conducted on, I think, "meta-analytic" residuals results as suggested in Nakagawa and Santos 2012. One could use such residuals to conduct the trim and fill method and see how much the mean could move (see Nakagawa and Santos 2012). One should remember the funnel asymmetry could be caused by the presece of heterogeniety. See:*

>Egger, M., G. Smith, M. Schneider, and C. Minder. 1997. Bias in metaanalysis detected by a simple, graphical test. \textit{Br Med J} 315:629 - 634.

Thanks -- we now **remind the reader that funnel plot asymmetry is not decisive evidence** for publication bias, because it can also result from unexplained heterogeneity in the original effect sizes. We have elected not to implement trim-and-fill since the method seems to have fallen into disfavour among many readers, and because we are unsure how to correctly implement it using the REML- and Bayesian methods we used. NB that there is no method for trim-and-fill in mixed meta-analysis in the popular R package `metafor` (which we used), suggesting the method is not simple to implement.

@@

Yes, and we have now included this information in the figure caption. Thank you for highlighting this.

>*6 --- the title - do the authors include "a systematic review" - so "a systematic reveiw and meta-analysis" - these two things are diferent - see:*

>Nakagawa, S., and R. Poulin. 2012. Meta-analytic insights into evolutionary ecology: an introduction and synthesis. \textit{Evolutionary Ecology} 26:1085-1099.

We agree, and we have changed the title to "Sexual selection improves population fitness: a systematic review and meta-analysis".  **DO THIS**

### 2018-12-29 Manuscripts/Manuscript_MetaAnalysis.Rmd
luke changes

A number of factors might influence the strength and sign of the correlation between sexual selection and population fitness. First, the genetic correlation between female fecundity and male mating/fertilisation success varies in sign and magnitude between species [@RN298] and even between conspecific populations [@RN201], implying that sexual selection on males increases mean female fitness in some species and populations but not others. These inconsistencies could derive from differences in allele frequencies, or environmental differences that alter how genotype relates to phenotype and fitness. Second, it has been hypothesised that populations should display a more positive genetic correlation between male and female fitness – and thus potentially between mating/fertilisation success and population fitness – in novel or fluctuating environments, relative to stable environments [@RN187; @RN173; @RN74; @RN257]. This is because stable environments create consistent selection, preferentially eroding genetic variation at sexually-concordant loci (*i.e.* loci where the fittest genotype is the same in both sexes) and leaving behind variation at sexually antagonistic loci. We know of no systematic reviews testing this latter theory, though it is has motivated several recent empirical tests [*e.g.* @RN187; @RN200; @RN254], and is relevant to conservation genetics.

@@

We retrieved 459 effect sizes from 65 studies. 92 effect sizes were collected from populations evolving under stressful conditions, while 337 were measured for those evolving in benign conditions. 189 of the effect sizes came from measurements made on males, 219 on females, and the remaining 51 from measurements of a mixed-sex sample of individuals. Most effect sizes in our dataset came from studies that manipulated sexual selection by completely removing it in one treatment via enforced random monogamy ($n$ = 241); other effect sizes ($n$ = 218) derived from alternative manipulations, such as changing the adult sex ratio. In total, we obtained effect sizes for 20 different fitness traits, with reproductive success ($n$ = 156) and offspring viability ($n$ = 56) being the most commonly-measured traits. We classified 216 effect sizes as direct measures of fitness, 141 as indirect, and the remaining 102 effect sizes as ambiguous (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}). Specifically, direct measures were components of reproduction or long-term viability (*e.g.*, reproductive success, offspring viability, and extinction rate), indirect measures were traits often used as a proxy of fitness but that do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production); and ambiguous measures were those reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration, and early fecundity). \href{https://justincally.github.io/SexualSelection/#tables_of_sample_sizes}{Tables S4-S5} give a detailed description of our dataset.\phantomsection

>>>>

A number of factors might influence the strength and sign of the correlation between sexual selection and population fitness. First, the genetic correlation between female fecundity and male mating/fertilisation success varies in sign and magnitude between species [@RN298] and even between conspecific populations [@RN201], implying that sexual selection on males increases mean female fitness in some species and populations but not others. These inconsistencies could derive from differences in allele frequencies, or environmental differences that alter how genotype relates to phenotype and fitness. Second, it has been hypothesised that populations should display a more positive genetic correlation between male and female fitness – and thus potentially between mating/fertilisation success and population fitness – in novel or fluctuating environments, relative to stable environments [@RN187; @RN173; @RN74; @RN257]. This is because stable environments create consistent selection, preferentially eroding genetic variation at sexually-concordant loci (*i.e.* loci where the fittest genotype is the same in both sexes) and leaving behind variation at sexually antagonistic loci. We know of no systematic reviews of this latter theory, though it is has motivated several recent empirical tests [*e.g.* @RN187; @RN200; @RN254], and is relevant to conservation genetics.

@@

We retrieved 459 effect sizes from 65 studies. 92 effect sizes were collected from populations evolving under stressful conditions, while 337 were measured for those evolving in benign conditions. 189 of the effect sizes came from measurements made on males, 219 on females, and the remaining 51 from measurements of a mixed-sex sample of individuals. Most effect sizes in our dataset came from studies that manipulated sexual selection by completely removing it in one treatment via enforced random monogamy ($n$ = 241); other effect sizes ($n$ = 218) derived from alternative manipulations, such as changing the adult sex ratio. In total, we obtained effect sizes for 20 different fitness traits, with reproductive success ($n$ = 156) and offspring viability ($n$ = 56) being the most commonly-measured traits. We classified **216 effect sizes as direct measures of fitness, 141 as indirect, and the remaining 102 effect sizes as ambiguous** (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}). Specifically, direct measures were components of reproduction or long-term viability (*e.g.*, reproductive success, offspring viability, and extinction rate), indirect measures were traits often used as a proxy of fitness but that do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production); and ambiguous measures were those reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration, and early fecundity). \href{https://justincally.github.io/SexualSelection/#tables_of_sample_sizes}{Tables S4-S5} give a detailed description of our dataset.\phantomsection

### 2018-12-29 meta_analysis_sexual_selection_pop_fitness.Rmd
luke changes

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
```

@@

**Study ID**: An ID given to the published paper the effect size is sourced from (n=65).

**Group ID**: An ID given to the research group that may have published several papers on the same species usuing the same or very similar experimental setup. [Was not use in analysis]

@@

**Table S9** In some instances it may be beneficial to the reader to obtain average effect sizes of each fitness trait **entirely independent** of other traits. For this reason we present a summary of independent model estimates for 16 fitness components with a sample size greater than 3 effect sizes (n>3). Unlike above where estimates were generated based on predictions from a single model, here we run individual meta-analyses for each fitness related trait. Independent models generally reduce the power and significance of some of the estimates with 'Extinction rate' and 'Ejaculate quality and production' the only two traits with p-values < 0.05.

@@

### Restricted analysis to just the higher-quality data

@@

```{r, message=FALSE, error = FALSE, warning=FALSE}
strict_dataset <- full_dataset %>% 
  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated")  %>% 
  mutate(Sex = relevel(Sex, ref = "M"),
         Environment = relevel(Environment, ref = "Unstressed"),
         Taxon = relevel(Taxon, ref = "Beetle"),
         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"))

model.complete <- rma.mv(g, V = var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon, 
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = strict_dataset)

@@

@@

  predict(model.complete, newmods=c(B, F, Stressed, Cricket, Fly, Guppy, Mite, Mouse, interaction1=interaction1, interaction2=interaction2))
}
# Get the predictions for each combination of moderators
predictions.complete <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed"),
                           Taxon = c("Beetle", "Cricket", "Fly", "Guppy", "Mite", "Mouse")))
predictions.complete <- cbind(predictions.complete, do.call("rbind", apply(predictions.complete, 1, get.predictions.complete))) %>%
  select(Sex, Environment, Taxon, pred, se, ci.lb, ci.ub) 
for(i in 4:7) predictions.complete[,i] <- unlist(predictions.complete[,i])

@@

Here we ask two key questions: Does sexual selection benefit populations in stressful environments more than benign environments? **AND** Do the benefits of sexual selection differ between the sexes? The only difference to the previous model is that `Taxon` is now treated as a random effect.

@@

```{r}
I2(model.complete2, strict_dataset$var.g) %>% pander(digits = 3)
```
These values indicate that 57.4 % of total heterogeneity is due to the **between study** heterogeneity and 37.4 % for **between outcome** heterogeneity between different outcomes. The total _I^2^_  is 94.7 %, a reasonably high _I^2^_ value. However this is relatively common in Ecology and Evolution total [@Senior_I2_2016].

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
knitr::opts_chunk$set(warning=FALSE, message=FALSE) # Suppress warnings in the HTML output

@@

**Study ID**: An ID given to the published paper the effect size is sourced from (n = 69).

**Group ID**: An ID given to the research group that may have published several papers on the same species usuing the same or very similar experimental setup. [Was not used in analysis]

@@

**Table S9** In some instances it may be beneficial to the reader to obtain average effect sizes of each fitness trait **entirely independently** of other traits. For this reason we present a summary of independent model estimates for 16 fitness components with a sample size greater than 3 effect sizes (n>3). Unlike above where estimates were generated based on predictions from a single model, here we run individual meta-analyses for each fitness related trait. Independent models generally reduce the power and significance of some of the estimates with 'Extinction rate' and 'Ejaculate quality and production' the only two traits with p-values < 0.05.

@@

### Restricted analysis of just the higher-quality data

@@

<!-- Note to Justin: here, I changed to just the 'direct' measures, and added the "Enforced Monogamy" predictor. You'll need to add the Bayesian equivalent, and alter the code for the figure etc. I think it's better this way, and the results don't appear to change in any major way -->

```{r, message=FALSE, error = FALSE, warning=FALSE}
# strict_dataset <- full_dataset %>% 
#   filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated")  %>% 
#   mutate(Sex = relevel(Sex, ref = "M"),
#          Environment = relevel(factor(Environment), ref = "Unstressed"),
#          Taxon = relevel(factor(Taxon), ref = "Beetle"))

strict_dataset <- full_dataset %>% 
  filter(Outcome.Class == "Direct" & Environment != "Not Stated")  %>% 
  mutate(Sex = relevel(Sex, ref = "M"),
         Environment = relevel(factor(Environment), ref = "Unstressed"),
         Taxon = relevel(factor(Taxon), ref = "Beetle"))

model.complete <- rma.mv(g, V = var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon + Enforced.Monogamy, 
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = strict_dataset)

@@

<!-- Bayesian equivalent is something like: -->

<!-- ```{r} -->
<!-- model.complete.bayesian <- brm(g | se(SE)  ~ 1 + Sex * Environment * Taxon + Enforced.Monogamy -->
<!--                   + (1|Study.ID)  -->
<!--                   + (1|Outcome),  -->
<!--                   family = "gaussian",  -->
<!--                   seed = 1, -->
<!--                   cores = 1, chains = 4, iter = 4000,  -->
<!--                   control = list(adapt_delta = 0.9999, max_treedepth = 15), -->
<!--                   data = strict_dataset %>% mutate(SE = sqrt(var.g))) -->
<!-- ``` -->

@@

  predict(model.complete, newmods=c(B, F, Stressed, Cricket, Fly, Guppy, Mite, Mouse, 1, interaction1, interaction2))
}
# Get the predictions for each combination of moderators
predictions.complete <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed"),
                           Taxon = c("Beetle", "Cricket", "Fly", "Guppy", "Mite", "Mouse")))
predictions.complete <- cbind(predictions.complete, do.call("rbind", apply(predictions.complete, 1, get.predictions.complete))) %>%
  select(Sex, Environment, Taxon, pred, se, ci.lb, ci.ub) 
for(i in 4:7) predictions.complete[,i] <- unlist(predictions.complete[,i])

@@

Here we ask two key questions: Does sexual selection benefit populations in stressful environments more than benign environments? **AND** Do the benefits of sexual selection differ between the sexes? The only difference to the previous model is that `Taxon` is now treated as a random effect. Note that this analysis again uses the strict dataset, containing only "direct" fitness measures and those where we were able to score the presence/absence of environmental stress.

@@

```{r warning=FALSE}
I2(model.complete2, strict_dataset$var.g) %>% pander(digits = 3)
```
These values indicate that 57.4 % of total heterogeneity is due to the **between study** heterogeneity and 37.4 % for **between outcome** heterogeneity between different outcomes. The total _I^2^_  is 94.7 %, a reasonably high _I^2^_ value. However this is relatively common in Ecology and Evolution total [@Senior_I2_2016].
